Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-02-09 cluster_paper/ms.tex
minor paper update

The GALAH DR3 target selection process is discussed in detail by
\citet{buder_galah_2020}.  The most relevant aspects for our projects
are that the ``main'' survey targeted $12.0<V<14.0$ stars at
$\delta<+10^\circ$, provided they were at least ten degrees from the
galactic plane.  The survey is spatially inhomogeneous\footnote{See
the footprint at
\url{https://www.galah-survey.org/news/announcing-galah-dr3}}. Special
targetting for stars in the TESS southern continuous viewing zone, and
for known open cluster members was also performed.  We identified the
candidate \cn\ members
for which spectra had been obtained by searching
the \texttt{GALAH\_DR3\_main\_allstar\_v1} catalog, after excluding
stars with the stellar parameter bit flags 1, 2, 3.  This excludes
spectra with unreliable broadening, low S/N, and unreliable wavelength
solutions (see Table~6 of \citealt{buder_galah_2020}).  Since our main
focus is measuring equivalent widths for the Li\,6708\ \AA line, these
were the most relevant bit flags for our purpose.  Of our \nkinematic
candidate \cn\ members, 106 had spectra in GALAH DR3.  51 were in the
``core''; 55 were in the ``halo''.

%/Users/luke/Dropbox/proj/earhart/results/lithium/kinematic_X_galah_dr3.csv
% https://docs.datacentral.org.au/galah/dr3/catalogue-data-access/
We downloaded the GALAH DR3 spectra for all 106 entries by doing PROCESS X.
We then measured the lithium equivalent widths using PROCESS Y.
We then concatenated the GALAH DR3 and Gaia-ESO results together.

>>>>

The GALAH DR3 target selection process is discussed in detail by
\citet{buder_galah_2020}.  The most relevant aspects for our project
are that the ``main'' survey targeted $12.0<V<14.0$ stars at
$\delta<+10^\circ$, provided the stars were at least ten degrees from the
galactic plane.  The survey is spatially inhomogeneous\footnote{See
the footprint at
\url{https://www.galah-survey.org/news/announcing-galah-dr3}}. Special
targeting for stars in the TESS southern continuous viewing zone, and
for known open cluster members was also performed.  We identified the
candidate \cn\ members
for which spectra had been obtained by searching
the \texttt{GALAH\_DR3\_main\_allstar\_v1} catalog, after excluding
stars with the stellar parameter bit flags 1, 2, 3.  This excludes
spectra with unreliable broadening, low S/N, and unreliable wavelength
solutions (see Table~6 of \citealt{buder_galah_2020}).  Since our main
focus is measuring equivalent widths for the Li\,6708\ \AA line, these
were the most relevant bit flags for our purpose.  Of our \nkinematic
candidate \cn\ members, 106 had spectra in GALAH DR3.  51 were in the
``core''; 55 were in the ``halo''.
77 had ``finite'' lithium, i.e., no lithium flag set.

%/Users/luke/Dropbox/proj/earhart/results/lithium/kinematic_X_galah_dr3.csv
% https://docs.datacentral.org.au/galah/dr3/catalogue-data-access/
We downloaded\footnote{Via \url{datacentral.org.au/services/download},
using the \texttt{sobject_id} identifiers.}
the GALAH DR3 spectra for all 106 entries.
We then measured the lithium equivalent widths using PROCESS Y.
We then concatenated the GALAH DR3 and Gaia-ESO results together.
